COG-ED Manuscript

### 2021-12-16 06_Paper/COG-ED/Manuscript.Rmd
implemented all changes for complete pipeline dfs

@@

@@

    # replace the RTs of incorrect trials with NA for better handling

    pipelines_data[[i]]$rt[pipelines_data[[i]]$correct == 0] <- NA

@@

            pipelines_data[[i]]$rt <- log10(pipelines_data[[i]]$rt)

@@

            pipelines_data[[i]]$rt <- 1/(pipelines_data[[i]]$rt)

@@

            pipelines_data[[i]]$rt <- sqrt(pipelines_data[[i]]$rt)
          }

@@

          pipemedian <- median(pipelines_data[[i]]$rt, na.rm = TRUE)
          pipemad <- mad(pipelines_data[[i]]$rt, na.rm = TRUE)

@@

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemedian + 2 * pipemad)
                                                               & pipelines_data[[i]]$rt > (pipemedian - 2 * pipemad))), ]

@@

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemedian + 2.5 * pipemad)
                                                               & pipelines_data[[i]]$rt > (pipemedian - 2.5 * pipemad))), ]
          } else if (pipeline_name[[1]][4] == "3") {

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemedian + 3 * pipemad)
                                                               & pipelines_data[[i]]$rt > (pipemedian - 3 * pipemad))), ]
          }

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])

@@

            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)
            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)

@@

              ifelse(length(which(pipelines_data[[i]]$level == x &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$level == x &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
                                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$level == x &
                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
                                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
        }

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                     & pipelines_data[[i]]$subject == pipesubject] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                                                                   & pipelines_data[[i]]$subject == pipesubject])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                     & pipelines_data[[i]]$subject == pipesubject] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                                                                & pipelines_data[[i]]$subject == pipesubject])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                     & pipelines_data[[i]]$subject == pipesubject] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                                                                  & pipelines_data[[i]]$subject == pipesubject])

@@

            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
          }
        }

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])

@@

            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)

@@

              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
        }

@@

      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ]) > 0,
             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ],
             pipelines_data[[i]] <- pipelines_data[[i]])

@@

      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ]) > 0,
             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ],
             pipelines_data[[i]] <- pipelines_data[[i]])

@@

    medianrt <- median(data_RT$rt[which(data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
                                 +(levelindex[i]-1)], na.rm = TRUE)

    newdata <- data.frame(subject = data_RT$subject[levelindex[i]],
                          level = data_RT$level[levelindex[i]],
                          medianrt = medianrt)
    rt <- rbind(rt, newdata)

@@

      # make a temporary copy of the rt data frame without 1-back

@@

      remove(h1b_data)

@@

  # make a temporary copy of the SV data frame

  h2a_data <- data_SV
  h2a_data$level <- as.factor(h2a_data$level)

@@

  h2b_data <- merge(dprime[c("subject", "level", "d")], data_nback, by = c("subject", "level"))

  # prepare temporary nfc-data frame for loop to feed into

    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]
    # define and invert items to be recoded
    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1

    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
                                           nfc = sum(nfc)))
  }
  data_nfc$subject[which(data_nfc$subject == "E12K08")] <- "E12K08_neu"

  h2b_data <- merge(h2b_data, data_nfc, by = "subject")

@@

  h2b_sub <- droplevels(subset(h2b_data[c("subject", "level", "sv", "d", "correct", "postcorrect", "rt", "nfc")],
                               subset = !is.na(rt)
                               & rt > 0.1))

@@

@@

    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]
    # define and invert items to be recoded
    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1

  # merge the NFC data frame into the AUC data frame by row

  h3_data <- merge(h3_data, data_nfc)

  # delete temporary variables

>>>>

  # change the name of a subject (it has the suffix "_neu" because the paradigm didn't start properly the first time)

  data_nback$subject[data_nback$subject == "E12K08_neu"] <- "E12K08"
  data_ED$subject[data_ED$subject == "E12K08_neu"] <- "E12K08"

@@

```{r NFCcomputation, echo=FALSE, message=FALSE, warning=FALSE}

    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]

    # define and invert items to be recoded

    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1

  # add the NFC scores trial-wise to the nback-data-frame for the multi-level-model

    data_nback$nfc[i] <- data_SV$nfc[data_SV$subject == data_nback$subject[i]]

  # remove the temporary variables

@@

@@

            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
              log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
              log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

@@

            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
              1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
              1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

@@

            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
              sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
              sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
          }

@@

          pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
          pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)

@@

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 2 * pipemad)
                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 2 * pipemad))), ]

@@

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 2.5 * pipemad)
                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 2.5 * pipemad))), ]
          } else if (pipeline_name[[1]][4] == "3") {

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 3 * pipemad)
                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 3 * pipemad))), ]
          }

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

@@

            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
        }

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])
            }

@@

            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
          }
        }

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

@@

              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

@@

            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)

@@

              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
        }

@@

      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ]) > 0,
             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ],
             pipelines_data[[i]] <- pipelines_data[[i]])

@@

      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ]) > 0,
             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ],
             pipelines_data[[i]] <- pipelines_data[[i]])

@@

    medianrt <- median(pipelines_data[["AARO"]]$rt[which(pipelines_data[["AARO"]]$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
                                 +(levelindex[i]-1)], na.rm = TRUE)

    newdata <- data.frame(subject = pipelines_data[["AARO"]]$subject[levelindex[i]],
                          level = pipelines_data[["AARO"]]$level[levelindex[i]],
                          medianrt = medianrt)
    rt <- rbind(rt, newdata)

@@

@@

      remove(h1b_data, rt)

@@

  # make a temporary copy of the data frame

  h2a_data <- unique(pipelines_data[["AARO"]][ ,c("subject","level","sv")])
  h2a_data$level <- as.factor(h2a_data$level)

@@

  h2b_data <- pipelines_data[["AARO"]]

@@

  h2b_sub <- droplevels(subset(h2b_data[c("subject", "level", "sv", "d", "correct", "postcorrect", "rt", "nfc")],
                               subset = !is.na(rt)))

@@

  # make a temporary copy of the data frame

  data_SV <- unique(pipelines_data[["AARO"]][ ,c("subject","level","sv")])
  data_SV$level <- as.factor(data_SV$level)

@@

  # add NFC values to data frame

  for (i in 1:(nrow(h3_data))) {

    h3_data$nfc[i] <- pipelines_data[["AARO"]]$nfc[pipelines_data[["AARO"]]$subject == h3_data$subject[i]]
